---
title: "Régression linéaire simple"
output: html_notebook
---

## Exercice 1
### 1.

```{r}
# Importing Data
data <- read.table("C:/Users/taha_/OneDrive - ine.inpt.ma/Coding/Academic-Projects/Regression Models/Data/exercice1.txt",sep="," ,fill = TRUE,header = TRUE)
head(data)
```


```{r}
# plot(Sunday ~ Daily, data = data,
xlab = "Diffusion quotidienne",
ylab = "Diffusion dominical",
main = "la diffusion dominicale par rapport à la diffusion
quotidienne",
pch = 20, cex.main=0.5, cex.lab=0.3, col = "grey")
DiffusionRegression<-lm(Sunday ~ Daily, data=data)
plot(Sunday ~ Daily, data = data,
xlab = "Diffusion quotidienne",
ylab = "Diffusion dominical",
main = " la diffusion dominicale par rapport à la diffusion
quotidienne",
pch = 20, cex.main=0.5, cex.lab=0.3, col = "grey")
abline(DiffusionRegression, col = "red")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}

```
